---
title: "Homework 1"
subtitle: "Rahul Hosalli (rh3064)"
output: html_document
---

# Dependent Libraries

```{r}
library(tidyverse)
```

# Problem 1

### Part A: Data Loading and Summary

The penguins data from the package `palmerpenguins` is loaded and described below.

```{r Problem_1}
data("penguins", package = "palmerpenguins")

skimr::skim(penguins)
```

The penguins dataset contains `r ncol(penguins)` columns and `r nrow(penguins)` rows. Information about the variables including variable type and summary statistics are included in the output of the `skim()` function above.

The mean flipper length is `r penguins %>% pull(flipper_length_mm) %>% mean(na.rm=TRUE)`.

### Part B. Plot and Output

The following code will produce a scatter plot of bill length (mm) on the x-axis and the flipper length (mm) on y. Penguins from different species have different colored points on the plot. The plot is outputted as a 10 X 7 .pdf in the project directory.

```{r}
penguin_plot <- 
  ggplot(data = penguins, 
         mapping = aes(x = bill_length_mm, y = flipper_length_mm, color = species)) +
  geom_point()

ggsave("penguin_plot.pdf", penguin_plot, width = 10, height = 7)
```

# Problem 2

## Part A: Dataframe Creation

The following code will produce a tibble of size 4 X 10, containing a random sample of size n=10, drawn from a normal distribution, a logic vector indicating if a member of the sample is greater than 0, a character vector of size 10 and a factor vector of size 10 with 3 levels.

```{r}

prob_2 <- tibble(
  numer_vec = rnorm(10),
  logic_vec = numer_vec > 0,
  charc_vec = c(paste("Example_", LETTERS[1:10], sep = "")),
  fact_vec = cut(numer_vec, 3, labels = c("Low", "Med", "High"))
)

prob_2
```
